### 2022-02-15 introduction/introduction.tex
toc

\chapter{Introduction}
\label{introduction}

@@

This approach proved useful: around 76\% of the simple proof goals can be
discharged automatically using Sledgehammer \cite{bgkku-16-larning-fact-selector}. However, there is
clearly some untapped potential in the approach as it communicates with
automatic theorem provers through a translation. To bridge this translation gap,
attempts were made to use higher-order automatic theorem provers instead of
first-order ones \cite{ns-13-leo2sh}. This proved unfruitful as state-of-the-art
higher-order theorem provers of the time were primarily designed for small and
tricky problems. On the other hand, problems coming from hammers consist of
mostly first-order formulas, are rather large, and mostly require simple
higher-order proof steps. Thus, from a standpoint of proof assistant ideal
automatic theorem prover fulfills the following wishlist:
\begin{enumerate}
  \item\label{it:fo} Performs as best first-order provers on first-order problems
  \item\label{it:ho} Supports higher-order logic and scales with the amount of higher-order axioms
  \item\label{it:size} Scales well with the size of the problem
\end{enumerate}
This brings us to the topic of this thesis: \emph{How can we develop a theorem provers that fulfills this wishlist?}

@@

In higher-order logic we can make statements about statements. More precisely,
we it treats Boolean terms (formulas) as first-class citizens, enabling us to
model some concepts in more natural manner. For example, we can naturally
represent statements such as ``what Jasmin says is true'' as $\forall x. \,
\cst{says}(\cst{jasmin}, x) \imp x$. The last stage is to support Boolean terms
as first-class citizens.

@@

  \item Following our approach of lifting efficient provers from
  first-order to higher-order logic, we went a step back in an effort to improve
  first-order provers. In particular, we looked at the most efficient approaches
  to simplify problems in propositional logic, a logic that disallows quantification,
  but it is decidable. We lifted some of these approaches to first-order logic
  and implemented them in Zipperposition.

\end{itemize}

\section{Publications and Thesis Structure}
\section{Related Work}

% \begin{abstract}
% Sample Abstract.
% \end{abstract}

% \blfootnote{This chapter is partly based on \faFileTextO~\emph{M. Beller. Toward an
%     Empirical Theory of Feedback-Driven Development, ICSE'18 (Student Research Competition)}~\cite{BellerSRC2018}.
% }

% \newpage

% \dropcap{T}his is a introductory page.

% \section{Background \& Context}
% In this thesis, you can reference pictures~\Cref{fig:devmodel} using Cleverref and circles \circled{5}.

% \begin{figure}[htb]
% 	\centering
% 	\includegraphics[width=0.65\columnwidth]{development_model_without_papers}
% 	\caption{The stages of the FDD model and their relationship to other
%           Software Engineering concepts.}
% 	\label{fig:devmodel}
% \end{figure}

% We also have lists:

% \begin{enumerate}
%   \item Static Analysis~\circled{3} examines program artifacts or
%     their source code without executing them~\cite{wichmann1995industrial}, while
%  \item Dynamic Analysis~\circled{4} relies on information gathered from their
%    execution~\cite{cornelissen2009systematic}.
% \end{enumerate}

% Or boxes:

% \begin{framed}
% This thesis is concerned with the empirical assessment of the state of the art of how developers
% drive software development with the help of feedback loops.
% \end{framed}

% Or code:
% \begin{lstlisting}[caption={\textsc{TrinityCore}},label={lst:e1}]
%  x += other.x;
%  y += other.y;
%  z += other.y;
% \end{lstlisting}

% I hope this helps you get started!
% Moritz

>>>>

\chapter{Introduction}
\setheader{Introduction}
\label{ch:intro}

@@

This approach proved useful: around 76\% of the simple proof goals can be
discharged automatically using Sledgehammer \cite{bgkku-16-larning-fact-selector}. However, there is
clearly some untapped potential in the approach as it communicates with
automatic theorem provers through a translation. To bridge this translation gap,
attempts were made to use higher-order automatic theorem provers instead of
first-order ones \cite{ns-13-leo2sh}. This proved unfruitful as state-of-the-art
higher-order theorem provers of the time were primarily designed for small and
tricky problems. On the other hand, problems coming from hammers consist of
mostly first-order formulas, are rather large, and mostly require simple
higher-order proof steps. Thus, from a standpoint of proof assistant ideal
automatic theorem prover fulfills the following wishlist:
\begin{enumerate}
  \item\label{it:fo} Performs as best first-order provers on first-order problems
  \item\label{it:ho} Supports higher-order logic and scales with the amount of higher-order axioms
  \item\label{it:size} Scales well with the size of the problem
\end{enumerate}
This brings us to the topic of this thesis: \emph{How to develop a prover fulfilling this wishlist?}

@@

In higher-order logic we can make statements about statements. More precisely,
we it treats Boolean terms (formulas) as first-class citizens, enabling us to
model some concepts in more natural manner. For example, we can naturally
represent statements such as ``what Jasmin says is true'' as $\forall x. \,
\cst{says}(\cst{jasmin}, x) \imp x$. The last stage is to support Boolean terms
as first-class citizens.
\pagebreak[2]

@@

  \item Following our approach of lifting efficient provers from
  first-order to higher-order logic, we went a step back in an effort to improve
  first-order provers. In particular, we looked at the most efficient approaches
  to simplify problems in propositional logic, a logic that disallows quantification,
  but it is decidable. We lifted some of these approaches to first-order logic
  and implemented them in Zipperposition. 
\end{itemize}

\section{Publications and Thesis Structure}

Starting from Chapter ????, every chapter of this thesis corresponds to a work that
was previously published. Work is presented in this thesis with the approval of coauthors.

\section{Related Work}
